---
title: "PIPS Functions"
author: "<Jakob Hedin>"
date: "2023-01-27"
output:
  html_document:
    df_print: paged
---

# This Rmd file documents the three functions available in this repository.

## remind_me

This function prints the dates and times for a number of exams during the upcoming semester. It takes no arguments. 

```{r}
remind_me <- function() {
  return(
    c(
      "PIPS Exam, 2023-02-03, 14:30 - 17:30",
      "Statistics 1 Exam, 2023-03-02, 11:00 - 13:00",
      "Statistics 2 Exam, 2023-03-31, 12:30 - 14:30",
      "Multilevel Analysis Exam, 2023-06-30, 12:00 - 14:00 "
    )
  )
}

remind_me()

```

## cheat

This function returns the answer to three of the week 3 R problems.
The function knows the answer to "3.1.1", to "3.1.9", and to "3.1.17". 
If provided with any other question (or other type of input), 
it results in an error message. 

```{r}
cheat <- function(questionnumber) {
  if (questionnumber == "3.1.1") {
    grades <- rnorm(63, 7.2, 1)
    hist(grades)
  }
  else if (questionnumber == "3.1.9") {
    library(ggstatsplot)
    ggbetweenstats(data = ToothGrowth, x = supp, y = len)
  }
  else if (questionnumber == "3.1.17") {
    print("The shortcut is Ctrl + Shift + A")
  }
  else {
    stop("Input must be a known question number of format 3.1.1")
  }
}

cheat("3.1.1")

```

## make_art
This function creates random art based on a subset of the jasmines package.
It takes three optional arguments, seed, color, and background (color). 
The arguments default to 1, "steelblue1" and "blue4".
The function relies mostly on the scene_bubbles function from the jasmines package
and uses several sampled numbers to set the various arguments,
creating a variety of different combinations. 
A seed can be set to ensure reproducible art, seed defaults to 1.
The generated art will be printed to the screen and saved as 
"random_art_test.png". This function requires the jasmines, dplyr, and ggplot2 packages to be installed. The function attempts to load the packages. 


```{r}

make_art <-
  function(seed = 1,
           color = "steelblue1",
           background = "blue4") {
    library(jasmines)
    library(dplyr)
    library(ggplot2)
    p0 <- use_seed(seed) %>%
      scene_bubbles(n = sample(1:150, 1),
                    grain = sample(1:2000, 1)) %>%
      unfold_tempest(iterations = sample(1:10, 1),
                     scale = sample(0.01:.099, 1)) %>%
      style_ribbon(color = color,
                   alpha = c(sample(0.05: 0.50, 1), sample(0.3:0.8,1)),
                   background = background)
    print(p0)
    ggsave(
      "random_art_test.png",
      p0,
      width = 50,
      height = 50,
      units = "cm"
    )
  }

make_art()
```


